The problem and promise of scale in animal social multilayer networks

### 2020-02-08 paper/manuscript.Rmd
reflow it
todo add examples with "individual A" "layer 2"

### Network metrics
<!-- TODO: expand + simplify + examples individual A, B etc -->
We used a series of metrics to characterize the multilayer networks, focusing on
the role of individuals, importance of individual layers and the similarity
of different layers. To measure the role of individuals, we calculated degree centrality and graph strength. Degree centrality is the number of direct connections an individual has to other individuals in a network layer. Graph strength is the degree weighted by the strength of association, in this case SRI, in each layer-specific season and landcover context <!-- TODO: citation for graph
strength?-->. Extending degree centrality, we calculated multidegree, the sum of degree centrality across layers, and neighbourhood, the sum of unique neighbours to each individual [@Berlingerio_2012; @Kivela_2014]. We evaluated the relevance and redundancy of layers by combining the multidegree and neighbourhood to calculate connective redundancy and layer relevance. Connective redundancy is the proportion of neighbours repeated in multiple layers, and layer relevance is the proportion of neighbours present in each layer compared to the neighbourhood for each individual
[@Berlingerio_2012].  Finally, we calculated the similarity of layers between
seasons, across landcover classes (e.g.: winter open compared to summer open)
using the Pearson correlation coefficient [@Br_dka_2018].

<!-- TODO: EVW "parallelism"? -->

>>>>

### Network metrics

<!-- TODO: expand + simplify + examples individual A, B etc --> 
<!-- TODO: EVW "parallelism"? -->

We used a series of metrics to characterize the multilayer networks,
focusing on the role of individuals, importance of individual layers and the
similarity of different layers. To measure the role of individuals, we
calculated degree centrality and graph strength. Degree centrality is the number
of direct connections an individual has to other individuals in a network layer.
Graph strength is the degree weighted by the strength of association, in this
case SRI, in each layer-specific season and landcover context <!-- TODO:
citation for graph strength?-->. Extending degree centrality, we calculated
multidegree, the sum of degree centrality across layers, and neighbourhood, the
sum of unique neighbours to each individual [@Berlingerio_2012; @Kivela_2014].
We evaluated the relevance and redundancy of layers by combining the multidegree
and neighbourhood to calculate connective redundancy and layer relevance.
Connective redundancy is the proportion of neighbours repeated in multiple
layers, and layer relevance is the proportion of neighbours present in each
layer compared to the neighbourhood for each individual [@Berlingerio_2012].
Finally, we calculated the similarity of layers between seasons, across
landcover classes (e.g.: winter open compared to summer open) using the Pearson
correlation coefficient [@Br_dka_2018].
